---
title: "Modules and applications"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Modules and applications}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: setup
#| include: false
#| eval: true
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 5,
  fig.height = 3.5,
  dpi = 140,
  fig.retina = TRUE
)
```

```{r}
#| label: pkgs
#| message: false
#| warning: false
library(mstsap)
library(lobstr)
library(fs)
```

This vignette covers the standalone shiny apps in the `mstsap` package.

## Apps from Mastering Shiny

Three of the applications in the `mstsap` package come from the [Modules section of Mastering Shiny](https://mastering-shiny.org/scaling-modules.html):

### `datasetApp()`

-   **`datasetApp()` contains the `datasetInput()` and `datasetServer()` module functions**

    -   `datasetInput()` displays the objects from the `datasets` package (`"dataset"`) matching `filter` argument (i.e., `is.data.frame`, `is.matrix`) and the table output (`"data"`) in the UI
   
    -   The `inputId` in the UI passes a `datasets` object (as `input$dataset`, a character string) to `datasetServer()`, which fetches and returns the object as a reactive via `get()` 
    
```{verbatim}
#| eval: false 
#| echo: true
█─datasetApp 
├─filter = NULL 
└─█─shinyApp 
  ├─ui = █─fluidPage 
  │      ├─█─datasetInput 
  │      │ ├─id = "dataset" 
  │      │ ├─filter = is.data.frame 
  │      │ └─█─selectInput 
  │      │   └─inputId = "dataset" 
  │      └─█─tableOutput 
  │        └─"data"
  └─server = █─function(input, output, session)
             └─█─data <- datasetServer(id = "dataset") 
               └─output$data <- renderTable(head(data()))
```

#### Reactive values 

The output from `reactiveValuesToList()` are displayed in the dev version of this application: 

```
$`dataset-dataset`
[1] "ability.cov"
```

The first `dataset` is from the module `id`, and the second is from the `inputId` (in the `selectInput()`).

<!--
    
```{r}
#| echo: false 
#| eval: false
#| comment: ""
#| include: true
lobstr::ast(
  datasetApp(filter = NULL,
    shinyApp(
      ui = fluidPage(
            datasetInput(id = "dataset", filter = filter,
              selectInput(inputId = "dataset")
              ),
            tableOutput("data")),
  server = function(`input, output, session`) {
    `data <- datasetServer(id = "dataset")`
    `output$data <- renderTable(head(data()))`
    }
   )
  )
)
```

-->
    
### `selectVarApp()`

-   **`selectVarApp()` contains the `datasetInput()`/`Server()` and `selectVarInput()`/`Server()` modules**
    - **`dataset` module:**
      -   [x] `datasetInput()` displays the objects from the `datasets` package (`"dataset"`) matching `filter` argument (i.e., `is.data.frame`, `is.matrix`) and the table output (`"data"`) in the UI
    
      -   [x] The `inputId` in the UI passes a `datasets` object (as `input$dataset`, a character string) to `datasetServer()`, which fetches and returns the object as a reactive with `get()`
    - **`selectVar` module:**
      -   `selectVarInput()` displays the variables (columns) in the returned `datasets` object from `datasetServer()` (as `"var"`) and the rendered output (as `"out"`)
    
      -   In `selectVarServer()`, the columns in the `data` returned from `datasetServer()` is filtered to those columns matching the `filter` argument (i.e., `is.numeric`), and the selected `"var"` is displayed in `"out"`

```{verbatim}
#| eval: false 
#| echo: true
█─selectVarApp 
└─█─shinyApp 
  ├─ui = █─fluidPage 
  │      ├─█─datasetInput 
  │      │ ├─id = "data" 
  │      │ ├─filter = is.data.frame
  │      │ └─█─selectInput 
  │      │   └─inputId = "dataset" 
  │      ├─█─selectVarInput 
  │      │ ├─id = "var" 
  │      │ └─█─selectInput 
  │      │   └─inputId = "var" 
  │      └─█─tableOutput 
  │        └─"out" 
  └─server = █─function(input, output, session)
             └─█─data <- datasetServer("data")
               █─var <- selectVarServer("var", data, filter = is.numeric)
               └─output$out <- renderTable(head(var()))
             
```


#### Reactive values 

The output from `reactiveValuesToList()` for both modules are displayed in the dev version of the application:

```
$`var-var`
[1] "Ozone"

$`data-dataset`
[1] "airquality"
```

- The first `"var"` is from the `selectVar` module `id`, the second is from the `selectInput()`

- `"data"` is from the `dataset` module `id`, the second is from the `selectInput()`

<!--

```{r}
#| echo: false 
#| eval: false
#| comment: ""
#| include: true
lobstr::ast(
  selectVarApp(
    shinyApp(
      ui = fluidPage(

      datasetInput(id = "data", filter = is.data.frame),

      selectVarInput(id = "var"),

      verbatimTextOutput("out")
        
  ), 
      server = function(`input, output, session`) {
        
        `data <- datasetServer("data")`
        
        `var <- selectVarServer("var", data, filter = filter)`

        `output$out <- renderPrint(head(var()))`
        
        }
      )
    )
  )
```

-->

### `selectDataVarApp()`

-   **`selectDataVarApp()` nests the `dataset` and `selectVar` modules *inside* the `selectDataVarUI()` and `selectDataVarServer()` functions:**
    - **`dataset` module:**
      -   [x] `datasetInput()` displays the objects from the `datasets` package (`"dataset"`) matching `filter` argument (i.e., `is.data.frame`, `is.matrix`) and the table output (`"data"`) in the UI
    
      -   [x] The `inputId` in the UI passes a `datasets` object (as `input$dataset`, a character string) to `datasetServer()`, which fetches and returns the object as a reactive with `get()`
    - **`selectVar` module:**
      -   [x] `selectVarInput()` displays the variables (columns) in the returned `datasets` object from `datasetServer()` (as `"var"`) and the rendered output (as `"out"`)
    
      -   [x] In `selectVarServer()`, the columns in the `data` returned from `datasetServer()` is filtered to those columns matching the `filter` argument (i.e., `is.numeric`), and the selected `"var"` is displayed in `"out"`

```{verbatim}
#| eval: false 
#| echo: true
█─selectDataVarApp 
└─█─shinyApp 
  ├─ui = █─fluidPage 
  │      └─█─sidebarLayout 
  │        ├─█─sidebarPanel 
  │        │ └─█─selectDataVarUI 
  │        │   ├─"var" 
  │        │   ├─█─datasetInput 
  │        │   │ ├─█─NS 
  │        │   │ │ ├─id 
  │        │   │ │ └─"data" 
  │        │   │ └─filter = is.data.frame 
  │        │   └─█─selectVarInput 
  │        │     └─█─NS 
  │        │       ├─id 
  │        │       └─"var" 
  │        └─█─mainPanel 
  │          └─█─verbatimTextOutput 
  │            └─"out" 
  └─server = █─function(input, output, session)
             ├─█─var <- selectDataVarServer(id = "var", filter = is.numeric)
             │ ├─data <- datasetServer(id = "data")
             │ ├─var <- selectVarServer(id = "var", data, filter = filter) 
             │ └─var 
             └─output$out <- renderPrint(head(var()))
```

<!--

```{r}
#| echo: false 
#| eval: false
#| comment: ""
#| include: true
lobstr::ast(
selectDataVarApp(
  shinyApp(
    ui = fluidPage(
    sidebarLayout(
      sidebarPanel(
        selectDataVarUI("var",
          datasetInput(NS(id, "data"), filter = is.data.frame),
          selectVarInput(NS(id, "var"))
          )
        ),
      mainPanel(
        verbatimTextOutput("out")
        )
    )
  ),
    
  server = function(`input, output, session`) {

    `var <- selectDataVarServer("var", filter)`(`data <- datasetServer("data")`,
      `var <- selectVarServer("var", data, filter = filter)`, `var`)
    `output$out <- renderPrint(head(var()))`

  }
  )
  ))
```
-->



