---
title: "selectVarApp tests"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{selectVarApp tests}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r}
#| label: setup
#| include: false
#| eval: true
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 5,
  fig.height = 3.5,
  dpi = 140,
  fig.retina = TRUE
)
# remotes::install_github("r-lib/lobstr", force = TRUE, quiet = TRUE)
# library(lobstr)
```

```{r}
#| label: pkgs
#| message: false
#| warning: false
library(mstsap)
library(lobstr)
library(testthat)
```


```{r}
#| label: test_cmt 
#| include: false
test_cmt <- function(test, msg) {
  cat("\n\t", glue::glue("  {test}: {msg}"), "\n")
}

```

## find_vars()

Test function (`is.double`)

```{r}
testthat::test_that("find_vars", {
    testthat::expect_equal(
    object = find_vars(datasets::airquality,
                            filter = is.double),
    expected = names(airquality)[vapply(airquality, is.double, logical(1))])
    test_cmt("find_vars", "is.double()")
})
```

Test function (`is.character`)

```{r}
testthat::test_that("find_vars", {
  testthat::expect_equal(
    object = find_vars(datasets::mtcars,
                            filter = is.character),
    expected = datasets::mtcars |>
      dplyr::select(where(is.character)) |>
      names())
  test_cmt("find_vars", "is.character()")
})
```

Test error: `state.abb` is a vector--pass `is.character` function to `filter`

```{r}
#| error: true
find_vars(data = datasets::state.abb, is.character)
```


```{r}
testthat::test_that("find_vars", {
  testthat::expect_error(object =
      find_vars(datasets::state.abb, filter = is.character))
  test_cmt("find_vars", "error: data")
})
```

Test error: pass `is.miracle` function to `filter`

```{r}
#| error: true
find_vars(data = datasets::mtcars, is.miracle)
```


```{r}
testthat::test_that("find_vars", {
  testthat::expect_error(object =
      find_vars(datasets::mtcars, filter = is.miracle))
  test_cmt("find_vars", "error: filter")

})
```

## selectVarServer() 

The `selectVarServer()` function has additional arguments, so the `args` list is used (with `reactive()`):

```{r}
shiny::testServer(selectVarServer,

  args = list(data = reactive(datasets::mtcars),
              filter = is.numeric), expr = {

  testthat::expect_true(
    object = is.reactive(data))
  test_cmt("selectVarServer", "is.reactive(data())")
})
```

Test passing different arguments to `find_vars()`

```{r}
shiny::testServer(selectVarServer,
  args = list(data = reactive(datasets::chickwts),
              filter = is.numeric), expr = {
  testthat::expect_equal(
    object = find_vars(data(), is.factor),
    expected = "feed")
  test_cmt("selectVarServer", "find_vars()")
})
```

Test passing `filter` and setting `input$var`:

```{r}
shiny::testServer(selectVarServer,
  args = list(data = reactive(datasets::chickwts),
              filter = is.numeric), expr = {

  session$setInputs(var = "weight")
  testthat::expect_equal(object = input$var,
      expected = "weight")
  test_cmt("selectVarServer", "input$var")
})
```

Test passing `filter`, setting `input$var`, and `session$returned()`:

```{r}
shiny::testServer(selectVarServer,
  args = list(data = shiny::reactive(datasets::chickwts),
              filter = is.numeric), expr = {
  session$setInputs(var = "feed")
  testthat::expect_equal(object = session$returned(),
      expected = datasets::chickwts[["feed"]])
  test_cmt("selectVarServer", "session$returned()")

})
```


## selectVarApp()

Test `is.reactive(var)`

```{r}
sv_app <- selectVarApp()
shiny::testServer(app = sv_app, expr = {
  session$setInputs(`var-var` = "Ozone",
                    `data-dataset` = "airquality")
  
  testthat::expect_true(object = is.reactive(var))
  test_cmt("selectVarApp", "is.reactive(var)")
})
```

Test the inputs with module namespaces 

```{r}
sv_app <- selectVarApp()
shiny::testServer(app = sv_app, expr = {
  session$setInputs(`var-var` = "Ozone",
                    `data-dataset` = "airquality")

  testthat::expect_equal(
    object = input$`var-var`,
    expected = "Ozone")
  test_cmt("selectVarApp", "input$`var-var`")

})
```

Test `data()` is reactive

```{r}
sv_app <- selectVarApp()
shiny::testServer(app = sv_app, expr = {
  session$setInputs(`var-var` = "Ozone",
                    `data-dataset` = "airquality")

  testthat::expect_true(object = is.reactive(data))
  test_cmt("selectVarApp", "is.reactive(data)")

})
```

Test `class()` of `data()`

```{r}
sv_app <- selectVarApp()
shiny::testServer(app = sv_app, expr = {
  session$setInputs(`var-var` = "Ozone",
                    `data-dataset` = "airquality")
  
  testthat::expect_true(
    object = is.data.frame(data()))
  test_cmt("selectVarApp", "is.data.frame(data())")

})
```

Test specific variables from `data()`

```{r}
sv_app <- selectVarApp()
shiny::testServer(app = sv_app, expr = {
  session$setInputs(`var-var` = "Ozone",
                    `data-dataset` = "airquality")

  testthat::expect_equal(
    object = data()[[input$`var-var`]],
    expected = airquality[["Ozone"]])
  test_cmt("selectVarApp", "data()[[input$`var-var`]]")

})
```
